D3692R1: How to Avoid OOTA Without Really Trying

### 2025-07-10 paper/ootavacuous.tex
ootavacuous: Restate benefits to full-up OOTA research in "Our Approach"
Reported-by: Alan Stern <stern@rowland.harvard.edu>
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

In short, this paper's contribution is to show how these
constraints allow real-world C++ implementations doing per-thread
analysis to avoid OOTA behavior easily,
%and not with minimal cost~\cite{PiezhaoOu2018OOTApapl},
in many cases with no cost at
all~\cite{PaulEMcKenney2023P3046R2/OOTAwithoutTrying}.
In addition, for those researchers working on identifying and avoiding
OOTA cycles, our results accommodate the needs of almost all C++
implementers, thus removing a key obstacle to the application of
high-complexity methods to this more general problem.
% \emph{@@@ Are these the right qualifiers?}

>>>>

In short, this paper's contribution is to show how these
constraints allow real-world C++ implementations doing per-thread
analysis to avoid OOTA behavior easily,
%and not with minimal cost~\cite{PiezhaoOu2018OOTApapl},
in many cases with no cost at
all~\cite{PaulEMcKenney2023P3046R2/OOTAwithoutTrying}.
In addition, our results simplify the job of researchers seeking
practical impact by allowing them ignore C++ implementers' need for
extreme simplicity and performance.
This in turn permits such researchers to focus on advanced topics such
as formal-verification tooling and evaluation of optimizations.
% \emph{@@@ Are these the right qualifiers?}
